Topological Equivariant Artist Model

### 2021-03-16 slides/main.tex
fixed nlab cite + ackwnolegemtn
D3 is explicit data structure
rework tools slides to add graphs

\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{bm}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}

@@

\subsection{Background}
\begin{frame}{Tools are tuned to the continuity of the date \cite{HeerSoftware2006,toryRethinkingVisualizationHighlevel2004}}
    \begin{columns}
        \column{0.33\textwidth}
        \begin{figure}
            \includegraphics[width=1\textwidth]{figures/intro/data_formatting.png}
            \caption{Based on fig~2.5 in Munzner's VAD\cite{munznerVisualizationAnalysisDesign2014}}
        \end{figure}

        \begin{enumerate}
            \item ggplot\cite{wickhamGgplot2ElegantGraphics2016a}
            \item protovis\cite{bostockProtoviz2009}, D3 \cite{bostockDataDrivenDocuments2011}
            \item vega\cite{satyanarayanDeclarativeInteractionDesign2014}, altair\cite{vanderplasAltairInteractiveStatistical2018}
        \end{enumerate}
        \pause
        \column{0.33\textwidth}
        \begin{figure}
            \includegraphics[width=1\textwidth]{figures/intro/landsat.png}
        \end{figure}
        \begin{enumerate}
            \item ImageJ\cite{schneiderNIHImageImageJ2012}, ImagePlot\cite{studiesCulturevisImageplot2021}\item Napari\cite{nicholas_sofroniew_2021_4533308}
        \end{enumerate}
        \pause
        \column{0.33\textwidth}
        \begin{figure}
            \includegraphics[width=1\textwidth]{figures/intro/dataset_diagram.png}
            \caption{Data Representation, MayaVi 4.7.2 docs\cite{DataRepresentationMayavi}}
        \end{figure}
        \begin{enumerate}
            \item Matplotlib\cite{hunterMatplotlib2DGraphics2007}, 
            \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveci2012vtk}, MayaVi\cite{RamachandranMayaVI2011}, ParaView\cite{ahrens2005paraview}, Titan\cite{brianwylieUnifiedToolkitInformation2009}
        \end{enumerate}
    \end{columns}
\end{frame}

@@

\begin{frame}{Structure of Components: Monoid \& Monoid Actions}
A monoid \monoid\ is a set with
\begin{description}
    \item[associative binary operator] $\ast:\monoid \times \monoid\rightarrow \monoid$
    \item[identity element] $e\in \monoid$ such that $e\ast a= a \ast e = a$ for all $a \in \monoid$. 
\end{description}
\pause
\begin{block}{left monoid action}
A set \dfiber\ with an action $\bullet: \monoid\times \dfiber \rightarrow \dfiber$ with the properties:
    \begin{align*}
        \textbf{associativity}\;& \text{for all } f,g \in \monoid \text{ and } x\in \dfiber,\, f\bullet(g\bullet x) = (f\ast g) \bullet x\\
        \textbf{identity}\;& \text{for all } x\in \dfiber, e\in \monoid,\,  e\bullet x = x 
    \end{align*}
\end{block}
\end{frame}

@@

\begin{frame}{Assembly Function Factory}
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/q_hat.png}
\end{figure}
\begin{equation}
\label{eq:qhat_q_s}
\vmarkd(\vsection(\dbasepoint))(\gbasepoint) \coloneqq \vmark((\vsectionpull)(\gbasepoint))
\end{equation} 
such \gbasepoint\ can be factored out when $\vpreimg = \gbasepoint$
\end{frame}

@@

    When artists share a base space 
    \begin{equation}
        \dbase_2 \hookrightarrow \dbase_1
    \end{equation}
    a composition operator can be defined such that the the artists can be considered to be acting on different components of the same section. 
\end{frame}
\begin{frame}{Equivalance class of artists}
    An approximation of the equivalence class of artists $\vartist^{\prime}$
    \begin{equation}
    \vartist \in \vartist^{\prime}: \vartist_{1} \equiv \vartist_{2}
    \end{equation}
    roughly treats two artists as equivalent if they 
    \begin{itemize}
        \item act on the same visual bundle \vtotal
        \item have the same assembly function \vmark 
        \item have the same continuity map \vindex 
    \end{itemize}
\end{frame}

>>>>

%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\usepackage{bm}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}

@@

\subsection{Background}
\begin{frame}{Tools are tuned to date continuity \cite{HeerSoftware2006}}
    \begin{columns}
            \column{0.33\textwidth}
            \begin{figure}
                \includegraphics[width=1\textwidth]{figures/intro/data_formatting.png}
                \caption{Based on fig~2.5 in Munzner's VAD\cite{munznerVisualizationAnalysisDesign2014}}
            \end{figure}
            \begin{enumerate}
                \item Tableau\cite{StoltePolaris2002,hanrahanVizQL2006,MackinlayShowme2007}
                \item ggplot\cite{wickhamGgplot2ElegantGraphics2016a}
                \item Vega\cite{satyanarayanDeclarativeInteractionDesign2014}, Altair\cite{vanderplasAltairInteractiveStatistical2018}
            \end{enumerate}
            \pause
            \column{0.33\textwidth}
            \begin{figure}
                \includegraphics[width=1\textwidth]{figures/intro/landsat.png}
            \end{figure}
            \begin{enumerate}
                \item ImageJ\cite{schneiderNIHImageImageJ2012}, ImagePlot\cite{studiesCulturevisImageplot2021}
                \item Napari\cite{nicholas_sofroniew_2021_4533308}
            \end{enumerate}
            \pause
            \column{0.33\textwidth}
            \begin{figure}
                \includegraphics[width=1\textwidth]{figures/intro/dataset_diagram.png}
                \caption{Data Representation, MayaVi 4.7.2 docs\cite{DataRepresentationMayavi}}
            \end{figure}
            \begin{enumerate}
                \item Gephi\cite{bastianGephiOpenSource2009}
                \item Graphviz\cite{ellsonGraphvizOpenSource2002}
                \item Networkx\cite{HagbergExploringNetwork2008}
            \end{enumerate}
    \end{columns}
\end{frame}

\begin{frame}{Visualizations are tuned to data continuinity\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.5\textheight]{figures/intro/dataset_diagram.png}
        \caption{Data Representation, MayaVi 4.7.2 docs\cite{DataRepresentationMayavi}}
    \end{figure}
    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007}, 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveci2012vtk}, MayaVi\cite{RamachandranMayaVI2011}, ParaView\cite{ahrens2005paraview}, Titan\cite{brianwylieUnifiedToolkitInformation2009}
    \end{enumerate}
\end{frame}

@@

\begin{frame}{Structure of Components: Monoid \& Monoid Actions}
A monoid \monoid\ is a set with
\begin{description}
    \item[associative binary operator] $\ast:\monoid \times \monoid\rightarrow \monoid$
    \item[identity element] $e\in \monoid$ such that $e\ast a= a \ast e = a$ for all $a \in \monoid$. 
\end{description}
\pause
\begin{block}{left monoid action}
A set \dfiber\ with an action\cite{nlab:action} $\bullet: \monoid\times \dfiber \rightarrow \dfiber$ with the properties:
    \begin{align*}
        \textbf{associativity}\;& \text{for all } f,g \in \monoid \text{ and } x\in \dfiber,\, f\bullet(g\bullet x) = (f\ast g) \bullet x\\
        \textbf{identity}\;& \text{for all } x\in \dfiber, e\in \monoid,\,  e\bullet x = x 
    \end{align*}
\end{block}
\end{frame}

@@

\begin{frame}{Assembly Function Factory}
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/q_hat.png}
\end{figure}
\begin{equation}\label{eq:qhat_q_s}
    \vmarkd(\vsection(\dbasepoint))(\gbasepoint) \coloneqq \vmark((\vsectionpull)(\gbasepoint))
\end{equation} 
such \gbasepoint\ can be factored out when $\vpreimg = \gbasepoint$
\end{frame}

@@

    When artists share a base space 
    \begin{equation}
        \dbase_2 \hookrightarrow \dbase_1
    \end{equation}
    a composition operator can be defined such that the the artists can be considered to be acting on different components of the same section. 
\end{frame}

\begin{frame}{Equivalance class of artists}
    An approximation of the equivalence class of artists $\vartist^{\prime}$
    \begin{equation}
    \vartist \in \vartist^{\prime}: \vartist_{1} \equiv \vartist_{2}
    \end{equation}
    roughly treats two artists as equivalent if they 
    \begin{itemize}
        \item act on the same visual bundle \vtotal
        \item have the same assembly function \vmark 
        \item have the same continuity map \vindex 
    \end{itemize}
\end{frame}
